Refining from the BON High-level Specification Language to the VHDL-AMS Hardware Description Language

### 2009-08-23 papers/BON_VHDL/paper.tex
change sections
continious work

\lstdefinelanguage{Bon} {
  morekeywords={require,ensure,feature,old,and,o,Q'slew,end,Result},
  morekeywords={class,delta,invariant,inherit,deferred,effective,NONE,make},
  morecomment=[l]{--}, 
  morecomment=[s]{/*}{*/}, 
  morestring=[b]", 
 literate=,
  showstringspaces=false
}

@@

\subsection{Seamlessness and Reversibility}
\emph{Seamlessness} is the use of a continuous process 
throughout the software lifecycle.
\emph{Reversibility} is the support for both forward and 
backward development process: from analysis to design 
and implementation, and back.
In VHDL-AMS, modelling represents an continious top-down-bottom-up
process. Top-down approach serves for design while bottom-up
serves for verification. The possibility of seamlessly translating 
changes made during a certain development phase back into earlier phases,
facilitates a stable and predictable environment and ensures the various 
models consistent with the code. Keeping in sync various models, documetation
and specification from forward progress to backward and redesign, preclude 
that design and implementation diverge to an inconsistent state.   
\subsection{Contracting}
\emph{Contracting} is the precise definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ). 
In VHDL-AMS \emph{simultaneous statement} represents analogue constraint of 
continuous-time waveform. In other words, simulator evaluates quantities such 
that the constraints specified by the simultaneous statements are satisfied. 
We admit that the constraint of waveform is nothing else than \emph{invariant}.
Another example of \emph{invariant} is conservation of energy law in which 
the summation of \arcoss quantities (\texttt{$\sum_{loop}$ across quatities =0}) 
around any closed path (loop) equals zero and the summation of through 
quantities (\texttt{$\sum_{node}$ through quatities =0}) at any node equals zero. 
Moreover, any predefined (implicite) attribute in VHDL 
has defined \emph{pre}/\emph{post condition} trought input/output 
parameters and theirs constraints. \\
Therefore as an approach of best modelling practices, and as the notation 
based on contract design, BON is the obvious choice 
for the our simulator.
Throughout this paper we will try to make this clear.

@@

\section{Mapping between BON and VHDL-AMS}

>>>>

\lstdefinelanguage{Bon} {
  morekeywords={require,ensure,feature,old,and,o,Q'slew,end,Result,INTEGER},
  morekeywords={class,delta,invariant,inherit,deferred,effective,NONE,make},
  morecomment=[l]{--}, 
  morecomment=[s]{/*}{*/}, 
  morestring=[b]", 
 literate=,
  showstringspaces=false
}

@@

\subsection{Seamlessness and Reversibility}
\emph{Seamlessness} is the use of a continuous process 
throughout the software lifecycle.
\emph{Reversibility} is the support for both forward and 
backward development process: from analysis to design 
and implementation, and back.
In VHDL-AMS, modelling represents an continious top-down-bottom-up
process. Top-down approach serves for design while bottom-up
serves for verification. The possibility of seamlessly translating 
changes made during a certain development phase back into earlier phases,
facilitates a stable and predictable environment and ensures the various 
models consistent with the code. Keeping in sync various models, documetation
and specification from forward progress to backward and redesign, preclude 
that design and implementation diverge to an inconsistent state. \emph{Seamlessness}
also plays important role in relating behaviours at differing levels of abstraction. 
For example, one may wish to relate the structural views of an A/D converter at the 
level of individual bits and at the level of busses. Therefore capturing similarities 
between the differing levels of abstractions far outweigh their inevitable differences, 
making it possible to obtain a continuous process that ensures a direct mapping between 
a formal specification and its software solution.

\subsection{Contracting}
\emph{Contracting} is the precise definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ). 
In VHDL-AMS \emph{simultaneous statement} represents analogue constraint of 
continuous-time waveform. In other words, simulator evaluates quantities such 
that the constraints specified by the simultaneous statements are satisfied. 
We admit that the constraint of waveform is nothing else than \emph{invariant}.
Another example of \emph{invariant} is conservation of energy law in which 
the summation of \arcoss quantities (\texttt{$\sum_{loop}$ across quatities =0}) 
around any closed path (loop) equals zero and the summation of through 
quantities (\texttt{$\sum_{node}$ through quatities =0}) at any node equals zero. 
Moreover, any predefined (implicite) attribute in VHDL 
has defined \emph{pre}/\emph{post condition} trought input/output 
parameters and theirs constraints. Furthermore any \emph{subtype} represents restricted
set of values from a base \emph{type}. The condition that determines which values are in the
\emph{subtype} may be \emph{contracted} by specifying characteristic predicate. 
For example, the \emph{subtype} \lstinlinenc|bit| of \lstinlinen|INTEGRER| may be defined as:\\
Therefore as an approach of best modelling practices, and as the notation 
based on contract design, BON is the obvious choice 
for the our simulator.
Throughout this paper we will try to make this clear.

\section{Mapping between VHDL-AMS and BON}

@@
